Matching bullets

### 2015-11-23 imaging-paper.Rnw
fiddling with ccf figure

Using (for now) a single crosscut across the surface, we extract the values and remove the class characteristics using a loess fit as before. This enables us to focus on the individual characterists. Striation marks show up in this representations as peaks and valleys. Figure~\ref{fig:cross100} shows lines of the surface crosscut at $x = 100$. A horizontal shift of one of the lines (result shown in (b)) emphasizes the strong similarities.
\hh{This horizontal shift is based on the cross-correlation between the two surface crosscuts. Let $f(t)$ and $g(t)$ define the values of the crosscut at $t$, then the cross-correlation between $f$ and $g$ at lag $k$ is defined as
\[
(f * g) (k) = \sum_t f(t+k) g(t),
\]
with suitable defined limits of the summation. 
}
\begin{figure}
<<ccf, echo=FALSE, fig.width = 7, fig.height = 3, out.width = '\\linewidth'>>=
lag <- ccf$lag[which.max(ccf$acf)]
qplot(x=ccf$lag, xend=ccf$lag, y = 0, yend= ccf$acf, geom="segment", colour = I("grey50")) + 
  theme_bw() + ylab("Correlation") + xlab("Lag k") +
  geom_segment(aes(x = lag, xend = lag, y = 0, yend =  max(ccf$acf)), colour="black") + 
  scale_x_continuous(breaks = c(-100, -50, lag, 0, 50, 100))
@
\caption{\label{fig:ccf}Cross-correlation between the two crosscuts shown in Figure~\ref{fig:crosscut} at lags between -100 and 100. At a lag of -10 the correlation peaks, indicating the largest amount of agreement between the crosscuts. Figure~\ref{fig:crosscutX} shows the lag-shifted crosscuts.}
\end{figure}

>>>>

Using (for now) a single crosscut across the surface, we extract the values and remove the class characteristics using a loess fit as before. This enables us to focus on the individual characterists. Striation marks show up in this representations as peaks and valleys. Figure~\ref{fig:cross100} shows lines of the surface crosscut at $x = 100$. A horizontal shift of one of the lines (result shown in (b)) emphasizes the strong similarities.
\hh{This horizontal shift is based on the cross-correlation between the two surface crosscuts. Let $f(t)$ and $g(t)$ define the values of the crosscut at $t$, then the cross-correlation between $f$ and $g$ at lag $k$ is defined as
\[
(f * g) (k) = \sum_t f(t+k) g(t),
\]
with suitable defined limits of the summation. % (because variances of $f$ and $g$ do not change, the above equation is proportional to the correlation). 
}
\begin{figure}
<<ccf, echo=FALSE, fig.width = 7, fig.height = 3, out.width = '\\linewidth'>>=
lag <- ccf$lag[which.max(ccf$acf)]
qplot(x=ccf$lag, xend=ccf$lag, y = 0, yend= ccf$acf, geom="segment", colour = I("grey50")) + 
  theme_bw() + ylab("Correlation") + xlab("Lag k") +
  geom_segment(aes(x = lag, xend = lag, y = 0, yend =  max(ccf$acf)), colour="black") + 
  scale_x_continuous(breaks = c(-100, -50, lag, 0, 50, 100),
                     minor_breaks = c(-75,-25,25, 75))
@
\caption{\label{fig:ccf}Cross-correlation between the two crosscuts shown in Figure~\ref{fig:crosscut} at lags between -100 and 100. At a lag of -10 the correlation peaks, indicating the largest amount of agreement between the crosscuts. Figure~\ref{fig:crosscutX} shows the lag-shifted crosscuts.}
\end{figure}
